Transforming Trash as an Artistic Act

### 2015-12-06 chapter4_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

[Transform] With the help of art (and artistic practices) discarded things can find a place in the society. (By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) With the help of art discarded things ---in the scope of thesis particularly paper trash--- can be transformed beyond the other industrial (or technological) methods.

[Work] Converting disposal things to multiple usage (or anything that is durable as noted in the rubbish theory). Realizing the alternative lifes of trash beyond their defined one shot life. Giving attention to the things. \comment{Inquerying concepts and perceptions that are not cared.} The work aims to liberate the imagination and change the way people see the trash.

[LIFE PRACTICE, CHANGES ON PEOPLE] Actually (It is questioned that) the effects of working with trash to the life practice. Working with trash is a convergence of behavioral patterns (attitudes toward to trash) and art making. The process effects one's life and lifestyle. (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) Looking for things and meanings in the normal course of life.

[DISTANCE] The purpose is not to build a thing that is produced from discarded material to watch it from a distance. The important thing is to interact with it. Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it. This work must change it. It must call the viewer to interact with it. Trash must be accepted.

@@

[ACT, COMMUNICATION, COLLABORATION] In this work it is claimed that the process of transformation of trash can be treated as artistic act. In the production of notebooks people collected papers from different places and location. During the collection phase, they have also collected them from other people. Communication and collaboration played significant role in the progress. (With this communication and collaboration the approach to the trash is explored in different cases.)

[NEW RESOURCE] Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics. Ignored and discarded nature of garbage, when rethought, becomes a fertile resource. Trash as a resource (as an artistic material). (City as a resource. Seeing the discarded items as a resource. Many artist approach to trash as resource. Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)

% TODO new comer. [POTENTIAL, new resource]
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
[building new things from ruin] \comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population. Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.

@@

% TODO new comer. Statement or approach.
\comment{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities. There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc. Even if they are excluded, there is also life for them.

@@

\todo{images are here.}

>>>>

\summary{Transform} 
With the help of art (and artistic practices) discarded things can find a place in the society. (By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) With the help of art discarded things ---in the scope of thesis particularly paper trash--- can be transformed beyond the other industrial (or technological) methods.

\summary{Work} 
Converting disposal things to multiple usage (or anything that is durable as noted in the rubbish theory). Realizing the alternative lifes of trash beyond their defined one shot life. Giving attention to the things. \comment{Inquerying concepts and perceptions that are not cared.} The work aims to liberate the imagination and change the way people see the trash.

\summary{Life practice, changes on people} 
It is questioned that the effects of working with trash to the life practice. Working with trash is a convergence of behavioral patterns (attitudes toward to trash) and art making. The process effects one's life and lifestyle. (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) Looking for things and meanings in the normal course of life.

\summary{Participation} 
The purpose is not to build a thing that is produced from discarded material to watch it from a distance. The important thing is to interact with it. Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it. This work must change it. It must call the viewer to interact with it. Trash must be accepted.

@@

\summary{Act, communication, collaboration}
In this work it is claimed that the process of transformation of trash can be treated as artistic act. In the production of notebooks people collected papers from different places and location. During the collection phase, they have also collected them from other people. Communication and collaboration played significant role in the progress. (With this communication and collaboration the approach to the trash is explored in different cases.)

\summary{New resource} 
Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics. Ignored and discarded nature of garbage, when rethought, becomes a fertile resource. Trash as a resource (as an artistic material). (City as a resource. Seeing the discarded items as a resource. Many artist approach to trash as resource. Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)

% TODO new comer. [POTENTIAL, new resource]
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\summary{Building new things from ruin} 
\comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population. Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.

@@

% TODO new comer. Statement or approach.
\summary{Trash and other discarded notions} 
From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities. There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc. Even if they are excluded, there is also life for them.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{Sax}
        \label{fig:exhibition1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{Violin}
        \label{fig:exhibition2}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{Violin}
        \label{fig:exhibition3}
    \end{subfigure}
    \caption{Installation try outs}
    \label{fig:exhibition}
\end{figure}

### 2015-12-06 chapter5.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

%
%
Many artworks are introduced. They have differences in terms of purpose and approached to the trash. Some of them only valued from its plastics effects (physicall properties). Some of them turned to the performative act.

%
%
\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this trasnformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them.

\comment{There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every proceses) new discard items are generated.}

%
%
\textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)

>>>>

%
%
Many artworks are introduced. They have differences in terms of purpose and approached to the trash. Some of them only valued from its plastics effects (physical properties). Some of them turned to the performance.

%
%
\summary{Evolution, Critics} During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this transformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them.

\comment{There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every process) new discard items are generated.}

%
%
\summary{Future Works} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
